Curiosity-Driven Development of Tool Use Precursors: a Robotic Model

### 2016-01-25 cogsci2016/paper.tex
figs
new results

	\paragraph{}
	Development of tool use: different properties \cite{guerin2013survey} (cite others?). 
	List of some properties: grounding of representation and planning based on a large amount of experiences, ongoing process of upgrading representations (others?).
	In that paper we will focus on one important property in the development of precursors of tool use which is the seemless progression 
	between successives phases of behavior with tools and objects which are called overlapping waves [Siegler]. 
	One behavioral description of the successives phases differentiate three phases \cite{guerin2013survey}.
	In the first phase the babies engage mostly in behavior without objects (babbling), in the second phase their behavior has shifted towards interaction with one object, and then interaction between objects.
	[more details: months, experiments]

@@

@@

				\item H0-MB: Random Motor Babbling
				\item H0-GB: Random Goal Babbling with a flat architecture learning $$M \rightarrow S_{Hand} \times S_{Stick_1} \times S_{Stick_2} \times S_{Object} \times S_{Boxes}$$
				\item H0-TR: The same architecture but with active goal babbling (my version of SAGG-RIAC)
				\item H1: Hierarchical architecture with Random Goal Babbling in each module, and choice of module that babbles based on interest ($\epsilon$-prop: probabilities proportional to interest but with $\epsilon=10\%$ of random choice). Choice of tool to use based on the maximum interest of the two modules that learn from the spaces of the tools to the object space, around the goal object point (competence progress on the k=10 NN).
				\item H1-GR: same as H1 but the choice of module to babble is $\epsilon$-greedy with $\epsilon=0.1$
				\item H1-CL: same as H1 but the choice of the tool to use is based on the maximum competence around the goal object point (competence of the NN)

@@

	\begin{figure*}[ht]
		\subfloat[]{\includegraphics[width=9cm]{./include/H1-log3-interests.png}}
		\subfloat[]{\includegraphics[width=9cm]{./include/H1-log3-obj-explo.png}}
		\caption{Condition H1. (a) Interests of each module. (b) Exploration of the object space: each dot is one point reached with the object at the end of one movement.}
		\label{res_interests}
	\end{figure*}

@@

	\begin{figure*}[ht]
		\subfloat[H1]{\includegraphics[width=9cm]{./include/choice_mod4_H1.png}}
		\subfloat[H1-CL]{\includegraphics[width=8.8cm]{./include/choice_mod4_H1-CL.png}}
		\caption{Chosen tool depending on object goal position. Blue points: long stick choice. Red points: small stick choice.}
		\label{res_choice}
	\end{figure*}

@@

	\subsection{H0 vs H1-GR vs H1}

@@

	\subsection{H1 vs H1-CL}

>>>>

	\paragraph{}
	Development of tool use: different properties \cite{guerin2013survey} (cite others?). 
	List of some properties: grounding of representation and planning based on a large amount of experiences, ongoing process of upgrading representations (others?).
	In that paper we will focus on one important property in the development of precursors of tool use which is the seamless progression 
	between successives phases of behavior with tools and objects which are called overlapping waves [Siegler]. 
	One behavioral description of the successives phases differentiate three phases \cite{guerin2013survey}.
	In the first phase the babies engage mostly in behavior without objects (babbling), in the second phase their behavior has shifted towards interaction with one object, and then interaction between objects.
	[more details: months, experiments]

@@

		\begin{figure}[h]
			\centering
			\subfloat{\includegraphics[width=2.8cm]{./include/mvt-16.pdf}}
			\subfloat{\includegraphics[width=2.8cm]{./include/mvt-32.pdf}}
			\subfloat{\includegraphics[width=2.8cm]{./include/mvt-49.pdf}}\\
			\hspace{-0.4cm}
			\subfloat{\includegraphics[width=8.8cm]{./include/dmp.pdf}}
			\caption{Exemple of one mouvement. Top: position of the arm at time steps 17, 33 and 50 along the $50$ steps movement. Bottom: value of the four Dynamical Movement Primitives during the movement.}
			\label{mvt}
		\end{figure}

@@

				\item F-RmB: Random Motor Babbling with a flat architecture learning $M \rightarrow S_{Hand} \times S_{Stick_1} \times S_{Stick_2} \times S_{Object} \times S_{Boxes}$
				\item F-RGB: Flat architecture, Random Goal Babbling
				\item F-AGB: The same architecture but with active goal babbling (my version of SAGG-RIAC)
				\item H-RGB-P-AMB: Hierarchical architecture with Random Goal Babbling in each module, and choice of module that babbles based on interest ($\epsilon$-prop: probabilities proportional to interest but with $\epsilon=10\%$ of random choice). Choice of tool to use based on the maximum competence of the two modules to reach the goal object point.
				\item H-RGB-GR-AMB: same as H-RGB-P-AMB but the choice of module to babble is $\epsilon$-greedy with $\epsilon=0.1$
				\item H-RGB-P-AMB-PGITC: same as H-RGB-P-AMB but the choice of the tool to use is based on the interest (global) of the two modules ($\epsilon$-prop).

@@

	\begin{figure*}[ht]
		\centering
		\subfloat[]{\includegraphics[width=9cm]{./include/H-RGB-P-AMB-log9-interests-100000.pdf}}
		\subfloat[]{\includegraphics[width=9cm]{./include/H-RGB-P-AMB-log9-obj-explo.pdf}}
		\caption{Condition H1. (a) Interests of each module. (b) Exploration of the object space: each dot is one point reached with the object at the end of one movement.}
		\label{res_interests}
	\end{figure*}

	\begin{figure*}[ht]
		\centering
		\subfloat[H-RGB-GR-AMB]{\includegraphics[width=8cm]{./include/H-RGB-GR-AMB-log15-events-100000.pdf}}
		\subfloat[H-RGB-P-AMB]{\includegraphics[width=8cm]{./include/H-RGB-P-AMB-log8-events-100000.pdf}}
		\caption{Behavioral measure}
		\label{res_ow}
	\end{figure*}

@@

	\begin{figure*}[ht]
		\subfloat[H-RGB-P-AMB]{\includegraphics[width=9cm]{./include/H-RGB-P-AMB-log9-choice_mod4.png}}
		\subfloat[H-RGB-P-AMB-PGITC]{\includegraphics[width=8.8cm]{./include/H-RGB-P-AMB-PGITC-log3-choice_mod4.png}}
		\caption{Chosen tool depending on object goal position. Blue points: long stick choice. Red points: small stick choice.}
		\label{res_choice}
	\end{figure*}

@@

	\subsection{F-AGB vs H-RGB-P-AMB vs H-RGB-GR-AMB}

@@

	\subsection{H-RGB-P-AMB vs H-RGB-P-AMB-PGITC}
